**The status of the microbial census: an update**

### 2015-11-09 Schloss_Census2_mBio_2015.Rmd
Integrate LaTeX stuff

---
title: "The status of the microbial census: an update"
output:
  md_document:
    variant: markdown_github
---

# The status of the microbial census: an update

Patrick D. Schloss<sup>1*</sup>, Rene Girard<sup>2</sup>, Thomas Martin<sup>2</sup>, Joshua Edwards<sup>2</sup>, J. Cameron Thrash<sup>2*</sup>

1.	Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI 48109, U.S.A.
2.	Department of Biological Sciences, Louisiana State University, Baton Rouge, LA 70803, U.S.A.

\* Correspondence: pschloss@umich.edu, thrashc@lsu.edu

@@

>>>>

---
title: "**The status of the microbial census: an update**"
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
csl: mbio.csl
fontsize: 11pt
geometry: margin=1.0in
---

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

inline_hook <- function(x){
	print(x)
	if(is.numeric(x)){
		if(abs(x - round(x)) < .Machine$double.eps^0.5){
			paste(format(x,big.mark=',', digits=0, scientific=FALSE))
		} else {
			paste(format(x,big.mark=',', digits=2, nsmall=2, scientific=FALSE))
		}

	} else {
    	paste(x)      
	}
}
knitr::knit_hooks$set(inline=inline_hook)
```
\vspace{35mm}

Patrick D. Schloss^1$\dagger$^, Rene Girard^2^, Thomas Martin^2^, Joshua Edwards^2^, and J. Cameron Thrash^2$\dagger$^

\vspace{40mm}

$\dagger$ To whom correspondence should be addressed: pschloss@umich.edu and thrashc@lsu.edu

1\. Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI 48109

2\. Department of Biological Sciences, Louisiana State University, Baton Rouge, LA 70803

\newpage
\linenumbers

@@

## Importance
